paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

for (i in 1:nrow(countycentroids)) {
  lat <- countycentroids$LATITUDE[i]
  long <- countycentroids$LONGITUDE[i]
  dists <- distHaversine(cbind(long, lat), cbind(providers$Lon, providers$Lat))
  countycentroids$distancetoprovider[i] <- min(dists)
}

>>>>

for (i in 1:nrow(countycentroids)) {
  lat <- countycentroids$LATITUDE[i]
  long <- countycentroids$LONGITUDE[i]
  dists <- distHaversine(cbind(long, lat), cbind(providers$Lon, providers$Lat))*3,958.8
  countycentroids$distancetoprovider[i] <- min(dists)
}
